\begin{abstract}
Modern LLM training pipelines have become increasingly complex, often relying on other models to generate training data, rewrite examples, filter corpora, label outputs, judge rewards, and guide development decisions. These recursive dependencies on upstream models are not captured by a single flat model card or dataset list, but are scattered across papers, code, dataset cards, model cards, and release notes. We introduce \system{}, an agentic system for reconstructing recursive, evidence-grounded dependency graphs of LLM releases from public artifacts. \system{} ingests heterogeneous public release artifacts---papers, model and dataset cards, code, and linked upstream artifacts---then recursively resolves and verifies model/data dependencies to produce an evidence-grounded dependency graph. From four public-artifact-rich LLM releases, \system{} recovers TODO verified dependencies with TODO\% precision, exceeding the strongest baseline's 299 verified dependencies. The recovered graph contains 2,844 artifacts organized into 2,545 identity clusters, 14,769 dependency edges, and 51,456 evidence anchors. Every target model has dozens to over 600 ancestors, and several extend 6 or more hops upstream, with the deepest chain reaching 11 hops. Beyond scale, the graph enables concrete audits, surfacing inherited license obligations, structural train/eval coupling, mismatches between released artifacts and trained-on artifacts, and documentation inconsistencies. Ultimately, \system{} turns scattered release evidence into an auditable model--model dependency graph, providing a practical tool for understanding what modern LLMs are built on.
\end{abstract}
