% =============================================================
% Qualitative findings — APPENDIX (supplementary).
% Findings demoted from the main text per reviewer feedback,
% retained here for completeness. Each item is multi-source and
% multi-hop, but is either too detailed, too narrow, or duplicative
% of a main-text finding to warrant main-text inclusion.
% =============================================================

\section{Additional Qualitative Findings}\label{appendix:findings}

The main text presents a curated subset of multi-hop, multi-source findings recovered by \system{}. This appendix collects the remaining findings that the graph also surfaces but that were demoted to keep the main qualitative section focused. We organize the appendix into the same five categories as the main text plus three additional categories (reward-model bootstrap chains, self-distillation, and cross-organization synthetic-data construction) that the graph makes legible as their own dependency classes.

\subsection{Additional hidden external-model dependencies}

\begin{itemize}
    \item \textbf{DR-Tulu inherits Nemotron-Math-v2 across three organizations through its base model.}
    DR-Tulu's released checkpoint chain is \texttt{rl-research/dr-tulu-8b} $\rightarrow$ \texttt{rl-research/DR-Tulu-SFT-8B} $\rightarrow$ \texttt{Qwen/Qwen3-8B}, and Qwen3-8B's training data includes \texttt{nvidia/Nemotron-Math-v2}. The recovered graph therefore surfaces an \texttt{rl-research} $\rightarrow$ \texttt{Qwen} $\rightarrow$ \texttt{NVIDIA} dependency chain that is invisible to anyone reading only the DR-Tulu paper or only the Qwen3-8B card.

    \item \textbf{OLMo-3-7B-Think-DPO trains on a Microsoft-originated tabular dataset.}
    Olmo-3-7B-Think-DPO has \texttt{LipengCS/Table-GPT} (the Microsoft Table-GPT dataset) as a training source, with downstream evaluation roles that include \texttt{microsoft/msr\_sqa}, \texttt{stanfordnlp/wikitablequestions}, and \texttt{sherlock-project/sherlock}. This Microsoft Research-originated artifact in an AI2 release is not foregrounded in either paper.

    \item \textbf{OLMo-3 inherits a Goedel-Prover$\rightarrow$gpt-oss-120b synthetic-data chain through Olmo-3.1.}
    Olmo-3-1125-32B's recovered ancestry includes a chain in which it was \texttt{generated\_by} Qwen/Qwen3-32B, which was itself \texttt{generated\_by} \texttt{openai/gpt-oss-120b}. The same gpt-oss-120b path also appears via \texttt{Goedel-LM/Goedel-Prover-V2-32B} for the Nemotron-3-Super formal-math pretraining slice. The graph thus surfaces gpt-oss-120b as a shared synthetic-data root that influences both AI2 and NVIDIA pipelines, even though neither model card names it as a primary teacher.
\end{itemize}

\subsection{Additional train/eval coupling cases}

\begin{itemize}
    \item \textbf{WildJailbreak and WildGuardMix have nearly symmetric train/eval roles within the AI2 family.}
    \texttt{allenai/wildjailbreak} appears as 25 training edges and 20 evaluation edges; \texttt{allenai/wildguardmix} appears as 22 / 22. This is a deliberate dual-role design rather than contamination, but the graph surfaces it as an explicit pattern: AI2 safety datasets are reused symmetrically across train and eval within the same product family.

    \item \textbf{OLMo-3 RL-Zero applies a ``spurious-reward decontamination check'' against an enumerated benchmark suite.}
    OLMo-3-7B-RL-Zero-Math, -Code, and -Mix carry edges flagging spurious-reward decontamination checks against GSM8K, GPQA, AIME 2024, AIME 2025, Minerva Math, ZebraLogic, and Omega-500. These edges are scattered across model and dataset cards plus paper figure captions, and the graph aggregates them into a single audit-ready set of evaluation sentinels.

    \item \textbf{Nemotron's Qwen3-Embedding-0.6B is used as an embedding-based decontamination filter.}
    A graph edge records that \texttt{Qwen/Qwen3-Embedding-0.6B} was used to encode problems and solutions and to drop any pretraining sample with cosine similarity $> 0.8$ against HumanEval, MBPP, CRUXEval, and LiveCodeBench. This embedding-mediated decontamination is invisible from the Nemotron-3-Super model card alone --- the filter model itself is the audit-relevant dependency.
\end{itemize}

\subsection{Additional license/provenance findings}

\begin{itemize}
    \item \textbf{Tulu-3's DPO data was generated by a wide cross-organization teacher panel.}
    \texttt{allenai/Llama-3.1-Tulu-3-8B-DPO}, \texttt{-70B-DPO}, and \texttt{-405B-DPO} together have 35--38 distinct upstream model generators per variant, including 01-ai/Yi family, Anthropic Claude 3.5 Sonnet (and v2), MosaicML/MPT-30B-Chat, GPT-3.5 / GPT-4 / GPT-4o family, Mixtral 8x7B / 8x22B, and InternLM. Each generator carries its own ToS or license; the resulting DPO mixture is therefore a license-agglomeration surface that no single Tulu card enumerates.

    \item \textbf{OpenAI gpt-oss-120b plays both subject and teacher roles across the graph.}
    \texttt{openai/gpt-oss-120b} appears as a downstream evaluated model, as a generator for synthetic Nemotron pretraining data ($\sim$23M solutions for Nemotron-3-Super code-concepts), as a transformation/judge node in OLMo-3, and as part of multi-org judge panels for Nemotron-3-Nano-Omni vision data. Its dual subject/teacher status raises non-trivial license-tracking questions that no individual model card exposes.
\end{itemize}

\subsection{Additional hidden judge/filter/synthesizer cases}

\begin{itemize}
    \item \textbf{Per-stage judge multiplicity (full counts).}
    Counting how many distinct stages of one product family share a single upstream judge:
    \texttt{openai/gpt-4.1} appears as judge/filter/generator in 22 distinct OLMo-3 stages;
    \texttt{Qwen/Qwen3-32B} in 20 OLMo-3 stages;
    \texttt{Qwen/QwQ-32B} in 9 OLMo-3 stages and 8 Nemotron-3 stages;
    \texttt{DeepSeek-AI/DeepSeek-R1-0528} in 8 Nemotron-3 stages and 5 Nemotron-Cascade stages.

    \item \textbf{Tulu-3 DPO 33--38 generators per variant.}
    The full generator panel for the Tulu-3 8B/70B/405B DPO checkpoints spans 33--38 distinct upstream models. Specific generators include 01-ai/Yi-34B-Chat, Yi-6B-Chat, Yi-1.5-34B, Yi-1.5-9B, Anthropic Claude 3.5 Sonnet and Sonnet v2, MosaicML/MPT-30B-Chat, MPT base variants, GPT-3.5-turbo (multiple snapshots), GPT-4, GPT-4o, and Mixtral-8x7B/8x22B-Instruct-v0.1.

    \item \textbf{OLMo-3-7B-Instruct-DPO has 38 distinct upstream generators including older 01-ai Yi releases.}
    The graph attributes 38 distinct generators to \texttt{allenai/Olmo-3-7B-Instruct-DPO}, including 01-ai/Yi-1.5-34B, Yi-1.5-9B, Yi-34B, Yi-9B, Gemma-3 family, Anthropic Claude, multiple GPT generations, and gpt-oss family. The presence of older Yi variants in a 2025-era release is not foregrounded in the OLMo-3 paper and emerges only from the DPO data card chain.

    \item \textbf{Multimodal Nemotron-3-Nano-Omni inherits 41 distinct upstream generators.}
    The vision/data subgraph for \texttt{nvidia/Nemotron-3-Nano-Omni-30B-A3B-Reasoning-BF16} attributes 41 distinct upstream generator/filter/transformer models, including Goedel-Prover-V2-32B, multiple Gemini-3 variants, GPT-4o, Qwen3 variants, MiniMax-M1, and Kimi K2.
\end{itemize}

\subsection{Additional released-artifact drift cases}

\begin{itemize}
    \item \textbf{Per-stage placeholder percentages quantified by joining YAML and data-prep scripts.}
    Per-edge descriptions in the recovered graph quantify the placeholder contributions: in \texttt{nvidia/Nemotron-RL-Super-Training-Blends}, DAPO-Math-17k contributes 1.36\% of the rlvr1 mix; Skywork-OR1-RL-Data contributes 5.44\% of the same mix; the same DAPO-Math-17k contributes 0.10\% to the Nano blend. These percentages are recoverable only by joining YAML mix-weight definitions with the upstream BytedTsinghua-SIA / Skywork dataset cards plus the \texttt{fill\_placeholders.py} data-prep script.

    \item \textbf{Decontamination-flagged dataset variants are first-class graph artifacts.}
    The recovered graph contains nodes such as \texttt{saumyamalik/persona-precise-if-r1-filtered-decontam}, \texttt{ai2-adapt-dev/numinamath\_tir\_math\_decontaminated}, and \texttt{allenai/evol\_codealpaca\_heval\_decontaminated} --- explicit ``decontaminated'' variants of upstream datasets. Their existence as first-class artifacts (rather than as a comment in a model card) shows that decontamination is now part of the artifact-level lineage.
\end{itemize}

\subsection{Additional documentation/code drift cases}

\begin{itemize}
    \item \textbf{The graph flags 60{,}708 cross-source conflicts that require multi-document reconciliation.}
    Across the recovered relations, \system{} flags 60{,}708 cross-source conflicts where two or more sources for the same relation disagree on either the description, identity attributes, or anchor evidence. Each conflict is small and resolvable in isolation, but the aggregate count shows that ``which source is authoritative for which fact'' is itself a property of the graph and not of any single document. (Many conflicts are benign identity/anchor disagreements; we report the raw count rather than a contamination claim.)

    \item \textbf{SmolLM3 trains on per-stage mix weights with sub-percent precision in YAML, far below paper-level granularity.}
    Recovered SmolLM3 training edges include exact mix weights such as \texttt{0.0017910} (peS2o), \texttt{0.0001791} (English Wikipedia), \texttt{0.0125367 / 0.0017910 / 0.0626834} (three MegaMath subsets), and per-language Stack-Edu shards (Python, Java, JavaScript, C, C++, C-Sharp, PHP, TypeScript, Swift, SQL, Ruby, Markdown, HTML, Rust). These specific weights are reproducible only by reading the YAML; the model card abstracts them away.

    \item \textbf{SmolLM3 inherits methodology, not just data, from upstream models.}
    Two recovered \texttt{inspired\_by} edges document method transfer rather than data transfer: SmolLM3-3B-Base ``uses intra-document attention masking similar to Llama 3'' (per the README), and ``FineMath's decontamination follows Qwen2.5-Math's 13-gram-overlap removal approach'' (per the FineMath card). These methodology-inheritance edges are a separate dependency class from data and weights, and are typically uncatalogued.
\end{itemize}

\subsection{Reward-model and judge bootstrap chains}

Modern post-training pipelines depend on judges and reward models that are themselves trained from upstream models and on upstream preference data. Beyond the Nemotron-3 GenRM chain in the main text, the graph surfaces additional RM/judge bootstrap structures.

\begin{itemize}
    \item \textbf{SmolLM2 is filtered by an external Llama-3-bootstrapped reward model.}
    \texttt{HuggingFaceTB/SmolLM2-1.7B-Instruct} carries a \texttt{filtered\_by} edge against \texttt{RLHFlow/ArmoRM-Llama3-8B-v0.1}: \texttt{smol-magpie-ultra} entries (consumed via SmolTalk) are scored by ArmoRM-Llama3-8B-v0.1 as the filter. This makes a Llama-3-derivative reward model an upstream filtering dependency for a HuggingFaceTB instruction model, only visible by following the SmolTalk pipeline.

    \item \textbf{Nemotron-3 also uses a parallel GenRM lineage initialized from Qwen3 and fine-tuned on commercial preference subsets.}
    A second GenRM node, \texttt{nvidia/Qwen3-Nemotron-235B-A22B-GenRM} (without the 2603 tag), is also \texttt{trained\_from} Qwen3-235B-A22B-Thinking-2507 and \texttt{trained\_on} \texttt{lmarena-ai/arena-human-preference-140k} subsets explicitly labelled commercially-friendly. The graph captures two parallel GenRM lineages within the same release, and both are upstream of Super's RL stack.

    \item \textbf{Nemotron-Cascade uses an internal reward model trained on Nemotron data.}
    A node \texttt{Nemotron-Cascade reward model (trained on nvidia ...)} appears as a recurring filter across at least four Nemotron-Cascade stages. The recursive lineage of this internal RM is opaque from any single model card and is exposed only via the Cascade dataset documentation.
\end{itemize}

\subsection{Self-distillation and within-family teacher chains}

Some training-time dependencies route a release back through its own family before reaching external models, complicating both attribution and reproducibility.

\begin{itemize}
    \item \textbf{Nemotron-3-Super was generated in part by its smaller sibling Nemotron-Nano-9B-v2.}
    A direct \texttt{generated\_by} edge identifies \texttt{nvidia/NVIDIA-Nemotron-Nano-9B-v2} as a generator for Nemotron-3-Super content (described as ``Nemotron-3 family member self-distillation''). The smaller sibling acting as a teacher for the larger model is a non-obvious data path and reverses the typical distill-from-bigger-to-smaller direction.

    \item \textbf{OLMo-3 family models appear as judges for other OLMo-3 stages.}
    The recovered graph attributes earlier OLMo-2 Instruct variants and \texttt{allenai/Olmo-3-1025-7B} itself as generators across multiple distinct OLMo-3 post-training stages each. Within-family self-bootstrapping is therefore a substantial fraction of the OLMo-3 RL ecosystem.
\end{itemize}

\subsection{Cross-organization synthetic-data construction}

The recovered graph shows that modern releases routinely use synthetic data generated by models from other organizations. The scale and concentration of this practice is a finding in itself.

\begin{itemize}
    \item \textbf{Cross-organization synthetic-data construction concentrates on a few high-value subsets.}
    Several training-data subsets are generated by extremely large model panels: \texttt{nvidia/NVIDIA-Nemotron-3-Super-120B-A12B-BF16} draws from 60 distinct generators; \texttt{Nemotron-3-Super-120B-A12B-NVFP4} from 53; \texttt{Nemotron-3-Nano-30B-A3B-BF16} and \texttt{-4B-BF16} from 51 each; \texttt{Nemotron-3-Nano-Omni-30B-A3B-Reasoning-BF16} from 41; AI2 \texttt{Olmo-3-7B-Instruct-DPO} from 38; \texttt{Llama-3.1-Tulu-3-8B-DPO} from 38. These large multi-org generator panels cluster around the post-training stages (DPO, RLHF, RLVR), suggesting that post-training is where the field-wide cross-organization synthetic-data dependency is most concentrated.

    \item \textbf{Some generator panels reach back to legacy chat models.}
    \texttt{allenai/WildLlama-7b-user-assistant} carries 31 distinct upstream generators including five different dated GPT-3.5-turbo snapshots (\texttt{0125}, \texttt{0301}, \texttt{0613}, \texttt{16k-0613}, plain). The graph thereby surfaces specific snapshot-level dependencies that mainstream papers compress to ``GPT-3.5'' --- a distinction that matters for reproducibility because each dated snapshot is a different model.

    \item \textbf{Datasets generated by 30+ models per release are routine.}
    Beyond the Nemotron flagship subsets, AI2 \texttt{Llama-3.1-Tulu-3-70B-DPO} and \texttt{-405B-DPO} pull from 35 and 33 distinct generators respectively; \texttt{allenai/Olmo-3-1025-7B} and \texttt{Olmo-3-1125-32B} each have 31 distinct generators; \texttt{nvidia/NVIDIA-Nemotron-3-Nano-30B-A3B-Base-BF16} has 30. Reading any single one of these as ``the model is finetuned on synthetic data from X'' loses the multi-org structure that the graph makes explicit.
\end{itemize}
